A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-10-20 documents/plm.tex
notes to self

@@

>>>>

\todo{Issue arising: I have called (below) the coefficients $a_{mm'}$.
However, they are different for every pixel $I_{mn}$.
That is, we do a separate optimization for every read-out pixel.
That means that really we should call the coefficients $a_{mnm'}$, right?
DFM:  Comments?}

@@

Once we have obtained the $a_{mm'}$ parameters corresponding to data point $I_{mn}$ by minimizing the training objective $\chi^2_{mn}$.
